### 2019-08-04 thesis.tex
*** empty log message ***

Since the pervasiveness of the plasma state in space came as a fact, plasma
physics became an essential component in the multidisciplinary framework of
astrophysics. At the same time, observations of space plasma phenomena have
been gaining increasing relevance in the advance of theoretical\cite{YZKS16,
  Tigik2017b}, computational\cite{Donnert2014,Pezzi2018}, and experimental
\cite{Howes2018,Peterson2019} plasma physics research.

>>>>

Since the pervasiveness of the plasma state in space came as a fact, plasma
physics became an essential component in the multidisciplinary framework of
astrophysics \cite{Parker1958a,Alfven1961,Gailitis1964}. At the same time,
observations of space plasma phenomena have been gaining increasing relevance
in the progress of theoretical, computational, and experimental plasma physics
research. The quality and quantity of space observations led to the development
of new theoretical models, and more advanced numerical schemes and experimental
set-ups in the area of plasma physics \cite{YZKS16,Donnert2014,Pezzi2018,
  Howes2018,Peterson2019}.
